paper_pdf

### 2020-03-21 paper_pdf.Rmd

prepared_data <- read_csv("/Users/faru/Documents/BIOSTATS_project/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))

census <- read_csv("/Users/faru/Documents/BIOSTATS_project/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]

@@

>>>>

prepared_data <- read_csv("/Users/faru/Documents/BIOSTATS_project/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))
food = read.csv("~/data/q1_and_q2.csv")
census <- read_csv("/Users/faru/Documents/BIOSTATS_project/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]

@@

# Question 2: Are local food choices associated with the Obesity rates?

### Are the food source variables associated with the obesity rates in 2008/09?

### Are the food source variables associated with the obesity rates in 2013/14?

The following are the assumptions of the two linear regressions we used:
Independence:
A common assumption across all inferential tests is that the observations in the sample are independent from each other.

Normality:
We have county level observations of over 3000 rows. As this value is relatively large, the central limit theorem will take effect and the non-normality does not matter. We also checked the residual qq plot for normality.

Constant Variance for obesity rate:
We assess the plot of residuals vs fitted values, and it shows clear evidence of non-constant variance. There is clearly a pattern of residuals that is undesirable to us. We used robust standard error to try to correct the non-constant variance problem.

```{r,echo=F,fig.height=6,fig.width=9,dev.args=list(pointsize=10)}
par(mfrow=c(1,2),mar=c(5,4,4,1))
fit2=lm(PCT_OBESE_ADULTS08~ GROCPTH09 +SUPERCPTH09 +CONVSPTH09  + SPECSPTH09 + WICSPTH08 +FFRPTH09 + FMRKTPTH09 + RECFACPTH09, data = food)
scatter.smooth(fit2$fitted.values,fit2$residuals,cex=0.5,col="gray")
qqnorm(fit$residuals)
qqline(fit$residuals)
```

```{r,echo=F,fig.height=6,fig.width=9,dev.args=list(pointsize=10)}
par(mfrow=c(1,2),mar=c(5,4,4,1))
fit=lm(PCT_OBESE_ADULTS13~ GROCPTH14 +SUPERCPTH14 +CONVSPTH14  + SPECSPTH14 + WICSPTH12 +FFRPTH14 + FMRKTPTH16 + RECFACPTH14 +FOOD_TAX14, data = food)
scatter.smooth(fit$fitted.values,fit$residuals,cex=0.5,col="gray")
qqnorm(fit$residuals)
qqline(fit$residuals)
```
